### 2025-05-20 manuscript/manuscript.Rmd
add Fisch citation

Two current areas of active research in fisheries stock assessment are defining and measuring 
reproductive potential for protogynous hermaphrodites [@alonzo2008importance; @brooks2008stock;
@alonzo2005sex] and incorporating genetic data into integrated models [@punt2020essential; @punt2024including].
Of particular interest is Close-Kin Mark-Recapture (CKMR) [@nielsen2001statistical;
@julius2001allele; @bravington2016close], a method that
uses genetic data to identify kin pairs in a sample and treats those
kin pairs as "recaptures" in a mark-recapture-like framework [see @casas2023review for a 
review of CKMR and its application to fisheries].
CKMR has been used to estimate absolute abundance for a number of marine and freshwater fish 
species with a range of reproductive strategies, including the
gonochoristic southern Bluefin tuna, *Thunnus thynnus*, [@bravington2016absolute; @davies2020next], 
semelparous Chinook salmon, *Oncorhynchus tshawytscha*, [@rawding2014genetic], and elasmobranchs which have a fixed-ratio 
reproductive strategy [@hillary2018genetic; @delaval2023evaluating].
Integrating CKMR into a stock assessment requires including the CKMR pseudolikelihood
[@bravington2016close] as one component in the stock assessment model.
This CKMR pseudolikelihood relates the observed number of genetically identified closely related pairs
(e.g., parent-offspring or half-sibling-pairs) in a sample to the
number expected given the size of the population. The expected
number of kin pairs is found by deriving a set of _kinship probabilities_, each one being
the probability that a pair of samples are close kin, given the size of the population and
additional information that describes the likelihood of an individual surviving and
reproducing over time relative to other individuals with similar demographic characteristics.

>>>>

Two current areas of active research in fisheries stock assessment are defining and measuring 
reproductive potential for protogynous hermaphrodites [@alonzo2008importance; @brooks2008stock;
@alonzo2005sex] and incorporating genetic data into integrated models [@punt2020essential; @punt2024including; @fisch2025expected].
Of particular interest is Close-Kin Mark-Recapture (CKMR) [@nielsen2001statistical;
@julius2001allele; @bravington2016close], a method that
uses genetic data to identify kin pairs in a sample and treats those
kin pairs as "recaptures" in a mark-recapture-like framework [see @casas2023review for a 
review of CKMR and its application to fisheries].
CKMR has been used to estimate absolute abundance for a number of marine and freshwater fish 
species with a range of reproductive strategies, including the
gonochoristic southern Bluefin tuna, *Thunnus thynnus*, [@bravington2016absolute; @davies2020next], 
semelparous Chinook salmon, *Oncorhynchus tshawytscha*, [@rawding2014genetic], and elasmobranchs which have a fixed-ratio 
reproductive strategy [@hillary2018genetic; @delaval2023evaluating].
Integrating CKMR into a stock assessment requires including the CKMR pseudolikelihood
[@bravington2016close] as one component in the stock assessment model.
This CKMR pseudolikelihood relates the observed number of genetically identified closely related pairs
(e.g., parent-offspring or half-sibling-pairs) in a sample to the
number expected given the size of the population. The expected
number of kin pairs is found by deriving a set of _kinship probabilities_, each one being
the probability that a pair of samples are close kin, given the size of the population and
additional information that describes the likelihood of an individual surviving and
reproducing over time relative to other individuals with similar demographic characteristics.
